\section{Clients}
\label{operation:Clients}

This subsection provides a detailed description of the client
mobile application's specific functionalities.

%%%%%%%%%%%%%%%%
\subsection{Request book loan}

When browsing books, the user has the option to request a book loan. The
request is sent to the main server, where it will wait for a librarian's input, whether
the loan is allowed or not.

\begin{description}

\item \textbf{Parameters: } ISBN number, Book name

\item \textbf{Precondition: } The library has at least one physical copy
available of the required book in store

\item \textbf{Post-condition: } 

\item \textbf{Output messages: } The client receives a confirmation of his
request being sent successfully

\item \textbf{Triggering:}
\begin{enumerate}
\item  User opens the list of available books via the interface button on the
bottom of the screen.

\item  He then proceeds to click on a book of his choice.

\item In the newly opened screen, the user clicks on the Request loan button.

\item When the user clicks Request loan, the request is sent to the server and
it then awaits for further confirmation.
\end{enumerate}
\end{description}

%%%%%%%%%%%%%%%%%
\subsection{Request book reservation}

 When browsing books, the user has the option to request a reservation for a
 book that is currently unavailable.
 The request is sent to the main server, where it will wait for a copy of the
 book to be returned back, and then the loan can be confirmed.

\begin{description}

\item \textbf{Parameters: } ISBN number, Book name, Date of reservation

\item \textbf{Precondition: } The library has no physical copies available for the
said book.

\item \textbf{Post-condition:}  

\item \textbf{Output messages:} The client receives a confirmation of his
reservation request being sent successfully.

\item \textbf{Triggering:}
\begin{enumerate}

\item User opens the list of available books via the interface button on the
bottom of the screen.

\item He then proceeds to click on a book of his choice.

\item The user can clicks on the Request reservation button on the newly opened
screen.

\item When the user clicks Request loan, the request is put in a queue,
awaiting for his turn to receive a copy of the book.
\end{enumerate}
\end{description}

%%%%%%%%%%%%%%%%
\subsection{Cancel book reservation}

 Apart from being able to send a book reservation request, the user also has the
 option to cancel one. The cancelation is effective immediately.

\begin{description}

\item \textbf{Parameters:} Book name

\item \textbf{Precondition:} The user has sent at least one request for a book
reservation.

\item \textbf{Post-condition:} The reservation request is removed from the
queue in the server.

\item \textbf{Output messages:} The user receives a message saying that his
cancelation has been successful and is returned to the reservation-browsing
screen.

\item \textbf{Triggering:}
\begin{enumerate}
\item Click on the Browse loans button at the bottom of the main screen.

\item Click on the Reservation button in the top half of the screen.

\item  In the list of reservations, click on the book's reservation that is to
be cancelled.

\item In the newly opened screen, click on the Cancel reservation button.

\item The user is returned back to the reservation list screen.

\end{enumerate}

\end{description}